The Castro AMR Simulation Code: Current and Future Developments

### 2019-10-10 astronum_2019_Castro/astronum-castro-2019.tex
soften

\castro\ implements both a second-order method (using a trapezoid rule
for the integral) and fourth-order method in space and time (using a
Simpsons rule for the integral and the spatial reconstruction of
\cite{mccorquodalecolella}).  We demonstrated that \castro\ achieves
the expected convergence on a wide variety of problems in
\cite{castro:sdc}.  At the moment, the method is limited to single
levels, but work is underway to extend this methodology to AMR.  For
problems where burning is important and can dominate the computational
expense, we expect this new SDC method will become the preferred
integration technique in the future.

>>>>

\castro\ implements both a second-order method (using a trapezoid rule
for the integral) and fourth-order method in space and time (using a
Simpsons rule for the integral and the spatial reconstruction of
\cite{mccorquodalecolella}).  We demonstrated that \castro\ achieves
the expected convergence on a wide variety of problems in
\cite{castro:sdc}.  At the moment, the method is limited to single
levels, but work is underway to extend this methodology to AMR.  For
problems where burning is important and can dominate the computational
expense, we hope this new SDC method will become the preferred
integration technique in the future.
